% ______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[overlapped, line]{resume}

% ______________________________________________________________________________________________________________________
\begin{document}


\name{\Large Song Wei}
\address{mobile: 832 964 6883; e-mail: 1983.song.wei@gmail.com}
\begin{resume}


  %% %  __________________________________________________________________________________________________________________
  %% \vspace{-25pt}\section{Objective}
  %% Seeking a job offer or internship in software development\\
  %% Availability: From Jan 15, 2009\\
  %% Visa Status: F1 with Employment Authorization Document (EAD) card\\

  % __________________________________________________________________________________________________________________
  % Education
  \vspace{-10pt}\section{Education}
         {\bf Master in Computer Science}, University of Houston, Houston, TX \hfill {\bf Aug. 2006 -- May. 2010}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Adviser:  Dr. Rong Zheng
         \item Thesis topic:  Multi Channel Multi Radio MAC For Wireless Mesh Network
         \item GPA: 3.412
         \end{list2}  \vspace{-5pt}

         {\bf Bachelor in Electronics Engineering}, \textbf{Tsinghua University}, Beijing, China \hfill {\bf Sep. 2002 -- June. 2006}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item GPA: 3.5
         \end{list2}  \vspace{-5pt}
         % __________________________________________________________________________________________________________________
         % Professional Experience
         \vspace{-15pt}\section{Experience}
         {\bf Software Developer}, Samsung \hfill {\bf April. 2012 -- Present}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Software Developer in Dallas Telecom Laboratory, Samsung Telecommunications, Richardson, TX
         \item \textbf{Firmware Over The Air Development}
           \begin{list2}
           \item New Android FOTA feature development
           \item FOTA algorithm improvement
           \item 
           \begin{list2}
           \item Patent pending
           \end{list2}
           \end{list2}
           \item Support WTL FOTA solution commercialization on Android
         \item \textbf{Mobile Framework Development}
           \begin{list2}
           \item Samsung addon and enchancement for Android framework
           \item Samsung tizen framework enchancement
           \end{list2}
         \item \textbf{New project support}
           \begin{list2}
           \item Collaboration in projects aiming new business areas. E.g.: healthcare
           \end{list2}          
         \end{list2}  \vspace{-5pt}

         {\bf Software Developer}, WorldLink, Inc \hfill {\bf May. 2010 -- April. 2012}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Consultant for Wireless Terminals Laboratory, Samsung Telecommunications, Richardson, TX
         \item \textbf{Firmware Over The Air Development}
           \begin{list2}
           \item New WTL Android FOTA feature development
           \item FOTA algorithm improvement
           \end{list2}
           \item Support WTL FOTA solution commercialization on Android
         \end{list2}  \vspace{-5pt}

         {\bf Software Developer Intern}, WorldLink, Inc \hfill {\bf Aug. 2009 -- Dec. 2009}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Consultant for Wireless Terminals Laboratory, Samsung Telecommunications, Richardson, TX
         \item \textbf{Firmware Over The Air Development and Testing}
           \begin{list2}
           \item Improved compression techniques for code update package
           \item Automated testing framework development
           \item Porting and Testing On BrewMP, Android platforms
           \item Qualcomm stack debugging using JTAG
           \end{list2}

         \end{list2}  \vspace{-5pt}


         {\bf Research Assistant}, Wiser Group, University of Houston, Houston, TX \hfill {\bf Aug. 2006 -- Aug. 2009}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item \textbf{Embedded Linux network driver development}
           \begin{list2}
           \item Developed an experimental {\bf Linux network driver} which controls multiple wireless interfaces on MAC level
           \item Testbed node development: OpenWrt on PC Engines Wireless Router Application Platform
           \item Testbed control framework in python
           \end{list2}
         \item \textbf{Wireless sensor development}
           \begin{list2}
           \item Prototyped wireless structure sensor network
           \item TinyOS 2.x on crossbow TelosB sensor
           \end{list2}
         \item \textbf{Optimization}
           \begin{list2}
           \item Robust minmax thin-plate spline optimization in \textbf{matlab}: to locate wireless handset from received wireless signal strengths
           \item Integer general bender's decomposition optimization in \textbf{python}: to assign channels and bit rates to wireless links and radios in wireless mesh network
           \end{list2}
         \item \textbf{NS2 and QUALNET programming}
           \begin{list2}
           \item NS2: duality between C++ and OTCL classes
           \item QUALNET: message driven parallel simulation in parsec
           \end{list2}
         \item \textbf{IT support}
           \begin{list2}
           \item Debian server administration
           \item Source control management
           \item CMS solution using Drupal
           \end{list2}
         \end{list2}  \vspace{-5pt}
%         \clearpage
         {\bf Teaching Assistant}, University of Houston, Houston, TX \hfill {\bf Spring 2008, Fall 2007}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Computer network system laboratory, fall 2007: ns2 simulation tutorial \& grading
         \item Computer networks, spring 2008: Linux network programming project tutorial \& grading
         \end{list2}  \vspace{-5pt}

         {\bf Team Leader}, Sheng Shi Hai Hua Digital Tech, Beijing, China \hfill {\bf Jun. 2005-Aug. 2005}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Led a team of 4 for an intelligent traffic information project
         \item Developed a web server using asp.net frontend + sql backend
         \item Utilized arcims map server and gpsOne service
         \end{list2}  \vspace{-5pt}

         {\bf Research Assistant}, Complex Engineered Systems Lab, Tsinghua University \hfill {\bf Feb. 2005 -- Jan. 2006}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item OSPF \& RIP routing simulation in c\#
         \item Investigated the possibility to use satellite broadcast network to provide inexpensive Internet content in rural districts of China
         \end{list2}  \vspace{-5pt}

         % __________________________________________________________________________________________________________________
         % Computer Skills

         \vspace{-15pt}\section{Skills} 
         \begin{tabbing}
           \= \hspace{1.5in}\= \kill
           \>{\bf programming} \>\textbf{c, python}, java, c++, lua, matlab\\
           \>{\bf development tools} \>\textbf{emacs}, eclipse, source insight\\
           \>{\bf experience} \>Linux kernel module development, Android framework, Android NDK, Android SDK\\
           \> \>Android bootloaders, GNU toolchain, ARM RVCT, Qualcomm stack\\ 
           \> \>cmake, OpenCV, tcpdump, Kismet, TRACE32 JTAG debugging, mysql\\
           \>{\bf IT skills} \> Linux server administration, git, perforce, svn, trac, gerrit, apache, drupal

         \end{tabbing}

         % __________________________________________________________________________________________________________________
         % Activities
         \vspace{-15pt}\section{Activities}
         Member, CougarCS, University of Houston  \hfill {\bf Aug 2006 - present}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Discussion groups, workshops and robocode competition
         \end{list2}  \vspace{-5pt}

         {\bf Team Leader}, Career Development Association, Tsinghua University \hfill {\bf Oct 2004 -  Dec 2005}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item Volunteer in career workshops and recruiting events
         \end{list2}  \vspace{-5pt}

         Member, Network Management Association, Tsinghua University \hfill {\bf Oct 2002 -  Oct 2003}\\
         \vspace{-10pt}      % suppress blank line after tabbing
         \begin{list2}
         \item News reporting
         \end{list2}  \vspace{-5pt}

         % __________________________________________________________________________________________________________________
         % Publications
         \vspace{-15pt}\section{Publication}

         Cunqing Hua, Song Wei and Rong Zheng,``Robust Channel Assignment for Link-level Resource Provisioning in Multi-radio Multi-channel Wireless Networks'', \textsl{Proceedings of the 16th IEEE International Conference on Network Protocols (ICNP), 2008} 

\end{resume}
\end{document}

% ______________________________________________________________________________________________________________________
% EOF

% LocalWords:  Kamil Wojcicki Wei EAD TX Aug Rong Zheng Tsinghua Beijing Sep NS
% LocalWords:  WorldLink Samsung WTL Android FOTA BrewMP Qualcomm JTAG Testbed
% LocalWords:  OpenWrt TinyOS crossbow TelosB minmax matlab bender's QUALNET ns
% LocalWords:  OTCL CMS Drupal Sheng Shi Hai Hua Jun frontend sql backend OSPF
% LocalWords:  arcims gpsOne java lua NDK SDK bootloaders toolchain RVCT cmake
% LocalWords:  OpenCV tcpdump Kismet mysql svn trac gerrit drupal CougarCS Oct
% LocalWords:  robocode Cunqing ICNP
